---
title: Retrieving and handling SHKR data with the package shkrdata
author: Oliver Nakoinz
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Retrieving and handling SHKR data with the package shkrdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
# str(knitr::opts_chunk$get())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  progress=FALSE,
  collapse = TRUE,
  comment = "#>"
  )

library(magrittr)
```

# Workflow

```{r ER diagram, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "ER diagram"}
library(DiagrammeR)  # http://rich-iannone.github.io/DiagrammeR/index.html   http://rich-iannone.github.io/DiagrammeR/graphviz_and_mermaid.html
dfgraph1 <- DiagrammeR::grViz("digraph G {
// 1. Daten/Objekte
// =============
shkr          [shape=box, label= 'shkr_list', fontname='FreeSans', fontsize=10, style=filled, fillcolor=Bisque, tooltip = 'list of tibbles']

shkr_fibulae  [shape=box, label= 'shkr_fibulae', fontname='FreeSans', fontsize=10, style=filled, fillcolor=DarkKhaki, tooltip = 'tibble of selected artefact types']

shkr_fibulae_comp  [shape=box, label= 'shkr_fibulae_comp', fontname='FreeSans', fontsize=10, style=filled, fillcolor=DarkKhaki, tooltip = 'tibble of selected artefact types completed with data from other loc levels']

shkr_fibulae_comp_coord   [shape=box, label= 'shkr_fibulae_comp_coord', fontname='FreeSans', fontsize=10, style=filled, fillcolor=DarkKhaki, tooltip = 'tibble of selected artefact types completed with data from other loc levels and completed coordinates']

shkr_fibulae_comp_coord_r  [shape=box, label= 'shkr_fibulae_comp_coord_r', fontname='FreeSans', fontsize=10, style=filled, fillcolor=DarkKhaki, tooltip = 'tibble of selected artefact types completed with data from other loc levels and completed coordinates; restricted to an area']

shkr_fibulae_graves  [shape=box, label= 'shkr_fibulae_graves', fontname='FreeSans', fontsize=10, style=filled, fillcolor=DarkKhaki, tooltip = 'tibble of selected artefact types completed with data from other loc levels and completed coordinates; restricted to an area and to a certain object type']

ts  [shape=box, label= 'ts', fontname='FreeSans', fontsize=10, style=filled, fillcolor=DarkKhaki, tooltip = 'tibble, contingence table, type spectrum']

dm  [shape=box, label= 'dm', fontname='FreeSans', fontsize=10, style=filled, fillcolor=DarkKhaki, tooltip = 'distance matrix']

snet  [shape=box, label= 'snet', fontname='FreeSans', fontsize=10, style=filled, fillcolor=DarkKhaki, tooltip = 'igraph']

Plot_snet              [shape=oval, label= 'plot:snet \n _man_cut_wnet', fontname='FreeSans', fontsize=10, style=filled, fillcolor=CornflowerBlue]

shkr2010_jma        [shape=oval, label= 'web:shkr2010', fontname='FreeSans', fontsize=10, style=filled, fillcolor=PaleVioletRed]

shkr2010_file              [shape=oval, label= 'file:shkr2010', fontname='FreeSans', fontsize=10, style=filled, fillcolor=PaleVioletRed]


// 2. Prozess/Methoden
// ================
shkr2010_download      [shape=diamond, label= 'shkrdata::shkr2010_download()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=Thistle, tooltip = 'download data from JMA server']

load_shkr2010      [shape=diamond, label= 'shkrdata::load_shkr2010()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=Thistle, tooltip = 'load shkr data into a list']


shkr_filter_loc10      [shape=diamond, label= 'shkrdata::shkr_filter_loc10()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightSteelBlue, tooltip = 'filter certain artefact types']

shkr_comp_loc10     [shape=diamond, label= 'shkrdata::shkr_comp_loc10()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightSteelBlue, tooltip = 'add information from the other loc levels to loc10']

shkr_coord_trans    [shape=diamond, label= 'shkrdata::shkr_coord_trans()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightSteelBlue, tooltip = 'transfere place coordinates to site coordinates for missing site coordinates']

shkr_filter_region      [shape=diamond, label= 'shkrdata::shkr_filter_region()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightSteelBlue, tooltip = 'restrict the data to a certain area']

shkr_filter_loc10_agg      [shape=diamond, label= 'shkrdata::shkr_filter_loc10_agg()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightSteelBlue, tooltip = 'restrict the data to a certain aggregation type such as graves or sites']

shkr_ts    [shape=diamond, label= 'shkrdata::shkr_ts()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightSteelBlue, tooltip = 'calculate the type spectrum using moin']

shkr_cul_dist     [shape=diamond, label= 'shkrdata::shkr_cul_dist()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightSteelBlue, tooltip = 'calculate the cultural distance matrix using moin']

shkr_net   [shape=diamond, label= 'shkrdata::shkr_net()', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightSteelBlue, tooltip = 'use the distance matrix as adjacency matrix']


plot         [shape=diamond, label= 'plot', fontname='FreeSans',fontsize=10, style=filled, fillcolor=LightBlue, tooltip = 'plot the igraph object']



// 3. Kanten/Datenfluss
// =================
shkr2010_jma  -> shkr2010_download
shkr2010_download -> shkr2010_file
shkr2010_file -> load_shkr2010
load_shkr2010 -> shkr
shkr -> shkr_filter_loc10
shkr_filter_loc10 -> shkr_fibulae
shkr_fibulae -> shkr_comp_loc10
shkr_comp_loc10 -> shkr_fibulae_comp
shkr_fibulae_comp -> shkr_coord_trans
shkr_coord_trans ->  shkr_fibulae_comp_coord
shkr_fibulae_comp_coord -> shkr_filter_region
shkr_filter_region -> shkr_fibulae_comp_coord_r
shkr_fibulae_comp_coord_r -> shkr_filter_loc10_agg
shkr_filter_loc10_agg -> shkr_fibulae_graves
shkr_fibulae_graves -> shkr_ts
shkr_ts -> ts
ts -> shkr_cul_dist
shkr_cul_dist -> dm
dm -> shkr_net
shkr_net -> snet
snet -> plot
plot -> Plot_snet

// 4. Subgraph
// ========

}", width = 600, height = 1700, engine = "dot") # engine = "neato")
dfgraph1
```

# Install

```{r inst, eval=FALSE}
library(devtools)
devtools::install_github("CRC1266-A2/moin")

devtools::install_gitlab("oliver.nakoinz/shkrdata.git")
# or
install.packages("./shkrdata_0.1.2.tar.gz", repos = NULL, type="source")
#utils::download.file("https://gitlab.com/oliver.nakoinz/shkrdata.git", "shkrdata")
```


# Download and load data

First, we have to download the data.

```{r download}
shkrdata::shkr2010_download(path = ".")
```

All filed of the downloaded data are loaded into a list containing tibbles.

```{r load}
shkr <- shkrdata::load_shkr2010("./shkr2010/")
```

/home/fon/daten/analyse/shkrdata/vignettes/shkr2010/loc_01.csv
                               ./vignettes/shkr2010/loc_01.csv

# Filter and complete data

Now, we select the the types, which we want to include into the analysis. The placeholder "." can be used in the type code.

```{r filter types}
shkr_fibulae <- shkrdata::shkr_filter_loc10(shkr, a = "A", b = "B31", c = "C", d = "D")
```

The next step is to include the information from all loc levels to the artefact tibble.

```{r complete levels}
shkr_fibulae_comp <- shkrdata::shkr_comp_loc10(shkr_fibulae, shkr)
```

Missing site coordinates are taken from the place coordinates.

```{r complete fill coordinates}
shkr_fibulae_comp_coord <- shkrdata::shkr_coord_trans(shkr_fibulae_comp)
```

The area of interest can be restricted by administrative units or by coordinates.

```{r filter region}
shkr_fibulae_comp_coord <- shkrdata::shkr_filter_region(shkr_fibulae_comp_coord, ftype = "loc05", a = 23133)
```

For our analysis only gravegoods are used.

```{r filter graves}
shkr_fibulae_graves <- shkrdata::shkr_filter_loc10_agg(shkr_fibulae_comp_coord, focus = "graves")
```

# Type spectrum

Now, the selection of data is completed and the spectrum of types can be calculated.

```{r type spectrum}
ts <- shkrdata::shkr_ts(shkr_fibulae_graves)
```

# Distance matrix

The is used to calculate a distance matrix.

```{r distance matrix}
dm <- shkrdata::shkr_cul_dist(ts)
```

# Network

The distance matrix is used as adjecancy matrix for producing an igraph object. 

```{r igraph}
snet <- shkrdata::shkr_net(dm)
```


Finally, we can plot the network.

```{r plot net}
plot(snet, edge.width = 6*igraph::E(snet)$weight)
```


# Query type list

It is also possible to print subtypes of a type.

```{r subtypes 1}
shkrdata::print_subtypes(shkr, typestring = "B311213", descr = FALSE)
```

Here "." can be used as wildcard for one digit.

```{r subtypes 2}
shkrdata::print_subtypes(shkr, typestring = "B3112.21", descr = FALSE)
```

The the string can also be searched in the type description.

```{r subtypes 3}
shkrdata::print_subtypes(shkr, typestring = "Ompha", descr = TRUE)
```


```{r cleaning, include=FALSE}
unlink("./shkr2010/", recursive=TRUE) 
```

